---
title: "chapter4 examples"
author: "Hao He"
date: "2022-10-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Relationships between words: n-grams and correlations
This chapter focuses on calculating and visualizing relationships between words in your text dataset
keywords: words co-occur; adjacent words

## Tokenizing by n-gram 
n: the number of words we wish to capture in each n-gram

### bigrams(n=2)
```{r}
library(dplyr)
library(tidytext)
library(janeaustenr)

austen_bigrams <- austen_books() %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

austen_bigrams
# here bigram as a token

#> # A tibble: 675,025 × 2
#>    book                bigram         
#>    <fct>               <chr>          
#>  1 Sense & Sensibility sense and      
#>  2 Sense & Sensibility and sensibility
#>  3 Sense & Sensibility <NA>           
#>  4 Sense & Sensibility by jane        
#>  5 Sense & Sensibility jane austen    
#>  6 Sense & Sensibility <NA>           
#>  7 Sense & Sensibility <NA>           
#>  8 Sense & Sensibility <NA>           
#>  9 Sense & Sensibility <NA>           
#> 10 Sense & Sensibility <NA>           
#> # … with 675,015 more rows

# these bigrams overlap: “sense and” is one token, while “and sensibility” is another.
```


```{r}
austen_bigrams %>%
  count(bigram, sort = TRUE)
```
a lot of the most common bigrams are pairs of common (uninteresting) words. It's better to separate them and remove cases that is in the list of stop-words.


```{r}
library(tidyr)

bigrams_separated <- austen_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

# remove words that are common by selecting words that is not a stop-word.
bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)

# new bigram counts:
bigram_counts <- bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)

bigram_counts
#> # A tibble: 28,975 × 3
#>    word1   word2         n
#>    <chr>   <chr>     <int>
#>  1 <NA>    <NA>      12242
#>  2 sir     thomas      266
#>  3 miss    crawford    196
#>  4 captain wentworth   143
#>  5 miss    woodhouse   143
#>  6 frank   churchill   114
#>  7 lady    russell     110
#>  8 sir     walter      108
#>  9 lady    bertram     101
#> 10 miss    fairfax      98
#> # … with 28,965 more rows
```

Then recombine the columns into one: now we have the most common bigrams not containing stop-words.
```{r}
bigrams_united <- bigrams_filtered %>%
  unite(bigram, word1, word2, sep = " ")

bigrams_united
```

In other analyses you may be interested in the most common trigrams(n=3):
```{r}
austen_books() %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3) %>%
  separate(trigram, c("word1", "word2", "word3"), sep = " ") %>%
  filter(!word1 %in% stop_words$word,
         !word2 %in% stop_words$word,
         !word3 %in% stop_words$word) %>%
  count(word1, word2, word3, sort = TRUE)

#> # A tibble: 6,141 × 4
#>    word1     word2     word3         n
#>    <chr>     <chr>     <chr>     <int>
#>  1 <NA>      <NA>      <NA>      13260
#>  2 dear      miss      woodhouse    20
#>  3 miss      de        bourgh       17
#>  4 lady      catherine de           11
#>  5 poor      miss      taylor       11
#>  6 sir       walter    elliot       10
#>  7 catherine de        bourgh        9
#>  8 dear      sir       thomas        8
#>  9 replied   miss      crawford      7
#> 10 sir       william   lucas         7
#> # … with 6,131 more rows
```

### Analyzing bigrams

This one-bigram-per-row format is helpful for exploratory analyses of the text.
we can look at the tf-idf (Chapter 3) of bigrams across Austen novels. These tf-idf values can be visualized within each book
```{r}
bigram_tf_idf <- bigrams_united %>%
  count(book, bigram) %>%
  bind_tf_idf(bigram, book, n) %>%
  arrange(desc(tf_idf))

bigram_tf_idf
```

plot the visualization
```{r}
bigram_tf_idf %>% 
  group_by(book) %>% 
  slice_max(tf_idf, n=15) %>%
  ungroup %>% 
  mutate(bigram = reorder(bigram, tf_idf)) %>% 
  ggplot(aes(tf_idf, bigram, fill = book)) +
  geom_col(show.legend = FALSE) +
  labs(x = "tf-idf", y = NULL) +
  facet_wrap(~book, ncol = 2, scales = "free")
  
```

### Using bigrams to provide context in sentiment analysis
```{r}
bigrams_separated %>%
  filter(word1 == "not") %>%
  count(word1, word2, sort = TRUE)
#> # A tibble: 1,178 × 3
#>    word1 word2     n
#>    <chr> <chr> <int>
#>  1 not   be      580
#>  2 not   to      335
#>  3 not   have    307
#>  4 not   know    237
#>  5 not   a       184
#>  6 not   think   162
#>  7 not   been    151
#>  8 not   the     135
#>  9 not   at      126
#> 10 not   in      110
#> # … with 1,168 more rows
```

```{r}
# use AFINN 
AFINN <- get_sentiments("afinn")

not_words <- bigrams_separated %>%
  filter(word1 == "not") %>%
  inner_join(AFINN, by = c(word2 = "word")) %>%
  count(word2, value, sort = TRUE)
# join bigrams_separated df with AFINN df, matching bigrams_separated$word2 to AFINN$word, so we have the sentiment score for words preceded by “not”
```

It’s worth asking which words contributed the most in the “wrong” direction.
To compute that, we can multiply their value by the number of times they appear (so that a word with a value of +3 occurring 10 times has as much impact as a word with a sentiment value of +1 occurring 30 times). This ways decrease the weight of common words and increase the weight of extreme words.
```{r}

library(ggplot2)

not_words %>%
  mutate(contribution = n * value) %>%
  arrange(desc(abs(contribution))) %>%
  head(20) %>%
  mutate(word2 = reorder(word2, contribution)) %>%
  ggplot(aes(n * value, word2, fill = n * value > 0)) +
  geom_col(show.legend = FALSE) +
  labs(x = "Sentiment value * number of occurrences",
       y = "Words preceded by \"not\"")

# mutate(word2 = reorder(word2, contribution)) ----- this way word2 variable is a factor, so bigrams in word2 variable can be seen on the plot
```
“not like” and “not help” were overwhelmingly the largest causes of misidentification. 

### other negating term that provides some context for the following word.
```{r}
negation_words <- c("not", "no", "never", "without")

negated_words <- bigrams_separated %>%
  filter(word1 %in% negation_words) %>%
  inner_join(AFINN, by = c(word2 = "word")) %>%
  count(word1, word2, value, sort = TRUE)
```

## Visualizing a network of bigrams with ggraph
```{r}
library(igraph)

# original counts
bigram_counts
#> # A tibble: 28,975 × 3
#>    word1   word2         n
#>    <chr>   <chr>     <int>
#>  1 <NA>    <NA>      12242
#>  2 sir     thomas      266
#>  3 miss    crawford    196
#>  4 captain wentworth   143
#>  5 miss    woodhouse   143
#>  6 frank   churchill   114
#>  7 lady    russell     110
#>  8 sir     walter      108
#>  9 lady    bertram     101
#> 10 miss    fairfax      98
#> # … with 28,965 more rows

# filter for only relatively common combinations
bigram_graph <- bigram_counts %>%
  filter(n > 20) %>%
  graph_from_data_frame()

bigram_graph
#> IGRAPH 014a232 DN-- 86 71 -- 
#> + attr: name (v/c), n (e/n)
#> + edges from 014a232 (vertex names):
#>  [1] NA      ->NA         sir     ->thomas     miss    ->crawford  
#>  [4] captain ->wentworth  miss    ->woodhouse  frank   ->churchill 
#>  [7] lady    ->russell    sir     ->walter     lady    ->bertram   
#> [10] miss    ->fairfax    colonel ->brandon    sir     ->john      
#> [13] miss    ->bates      jane    ->fairfax    lady    ->catherine 
#> [16] lady    ->middleton  miss    ->tilney     miss    ->bingley   
#> [19] thousand->pounds     miss    ->dashwood   dear    ->miss      
#> [22] miss    ->bennet     miss    ->morland    captain ->benwick   
#> + ... omitted several edges
```


for a basic graph we need to add three layers: nodes, edges, and text.
```{r}
library(ggraph)
set.seed(2017)

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)
```

polishing the plot
```{r}
set.seed(2020)

a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()

# edge_alpha aesthetic to the link layer to make links transparent based on how common or rare the bigram is
```

Note that this is a visualization of a Markov chain, a common model in text processing. In a Markov chain, each choice of word depends only on the previous word.


### Visualizing bigrams in other texts
create a function that collects our work on cleaning and visualizing bigrams on a text dataset, so we can easily perform it on other text datasets.

```{r}
library(dplyr)
library(tidyr)
library(tidytext)
library(ggplot2)
library(igraph)
library(ggraph)

count_bigrams <- function(dataset) {
  dataset %>%
    unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
    separate(bigram, c("word1", "word2"), sep = " ") %>%
    filter(!word1 %in% stop_words$word,
           !word2 %in% stop_words$word) %>%
    count(word1, word2, sort = TRUE)
}

## visualization via network graph
visualize_bigrams <- function(bigrams) {
  set.seed(2016)
  a <- grid::arrow(type = "closed", length = unit(.15, "inches"))
  
  bigrams %>%
    graph_from_data_frame() %>%
    ggraph(layout = "fr") +
    geom_edge_link(aes(edge_alpha = n), show.legend = FALSE, arrow = a) +
    geom_node_point(color = "lightblue", size = 5) +
    geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
    theme_void()
}

```



```{r}
# the King James version is book 10 on Project Gutenberg:
library(gutenbergr)
kjv <- gutenberg_download(10, mirror = "http://mirrors.xmission.com/gutenberg/")


library(stringr)

kjv_bigrams <- kjv %>%
  count_bigrams()

# filter out rare combinations, as well as digits
kjv_bigrams %>%
  filter(n > 40,
         !str_detect(word1, "\\d"),
         !str_detect(word2, "\\d")) %>%
  visualize_bigrams()
```


## countting & correlating pairs of words(*widyr*)
Except for adjacent words, words that tend to co-occur within particular documents or particular chapters also are useful, even if they don’t occur next to each other.

Most operations for finding pairwise counts or correlations *need to turn the data into a wide matrix first*.

The widyr package first ‘casts’ a tidy dataset into a wide matrix, performs an operation such as a correlation on it, then re-tidies the result.

### among sections

```{r}

# divided into 10-line sections
austen_section_words <- austen_books() %>%
  filter(book == "Pride & Prejudice") %>%
  mutate(section = row_number() %/% 10) %>%
  filter(section > 0) %>%
  unnest_tokens(word, text) %>%
  filter(!word %in% stop_words$word)

austen_section_words
#> # A tibble: 37,240 × 3
#>    book              section word        
#>    <fct>               <dbl> <chr>       
#>  1 Pride & Prejudice       1 truth       
#>  2 Pride & Prejudice       1 universally 
#>  3 Pride & Prejudice       1 acknowledged
#>  4 Pride & Prejudice       1 single      
#>  5 Pride & Prejudice       1 possession  
#>  6 Pride & Prejudice       1 fortune     
#>  7 Pride & Prejudice       1 wife        
#>  8 Pride & Prejudice       1 feelings    
#>  9 Pride & Prejudice       1 views       
#> 10 Pride & Prejudice       1 entering    
#> # … with 37,230 more rows
```


```{r}
library(widyr)

# count words co-occuring within sections
word_pairs <- austen_section_words %>%
  pairwise_count(word, section, sort = TRUE)

word_pairs
#> # A tibble: 796,008 × 3
#>    item1     item2         n
#>    <chr>     <chr>     <dbl>
#>  1 darcy     elizabeth   144
#>  2 elizabeth darcy       144
#>  3 miss      elizabeth   110
#>  4 elizabeth miss        110
#>  5 elizabeth jane        106
#>  6 jane      elizabeth   106
#>  7 miss      darcy        92
#>  8 darcy     miss         92
#>  9 elizabeth bingley      91
#> 10 bingley   elizabeth    91
#> # … with 795,998 more rows
```


words that most often occur with Darcy:
```{r}
word_pairs %>%
  filter(item1 == "darcy")
#> # A tibble: 2,930 × 3
#>    item1 item2         n
#>    <chr> <chr>     <dbl>
#>  1 darcy elizabeth   144
#>  2 darcy miss         92
#>  3 darcy bingley      86
#>  4 darcy jane         46
#>  5 darcy bennet       45
#>  6 darcy sister       45
#>  7 darcy time         41
#>  8 darcy lady         38
#>  9 darcy friend       37
#> 10 darcy wickham      37
#> # … with 2,920 more rows
```

### Pairwise correlation

examine correlation among words, which indicates how often they appear together relative to how often they appear separately.

 phi coefficient [common measure for binary correlation]
 
The focus of the phi coefficient is how much more likely it is that either both word X and Y appear, or neither do, than that one appears without the other.

The phi coefficient is equivalent to the Pearson correlation.

```{r}
# we need to filter for at least relatively common words first
word_cors <- austen_section_words %>%
  group_by(word) %>%
  filter(n() >= 20) %>%
  pairwise_cor(word, section, sort = TRUE)

word_cors
#> # A tibble: 154,842 × 3
#>    item1     item2     correlation
#>    <chr>     <chr>           <dbl>
#>  1 bourgh    de              0.951
#>  2 de        bourgh          0.951
#>  3 pounds    thousand        0.701
#>  4 thousand  pounds          0.701
#>  5 william   sir             0.664
#>  6 sir       william         0.664
#>  7 catherine lady            0.663
#>  8 lady      catherine       0.663
#>  9 forster   colonel         0.622
#> 10 colonel   forster         0.622
#> # … with 154,832 more rows


word_cors %>%
  filter(item1 == "pounds")


word_cors %>%
  filter(item1 %in% c("elizabeth", "pounds", "married", "pride")) %>%
  group_by(item1) %>%
  slice_max(correlation, n = 6) %>%
  ungroup() %>%
  mutate(item2 = reorder(item2, correlation)) %>%
  ggplot(aes(item2, correlation)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ item1, scales = "free") +
  coord_flip()
```


## visualize the correlations and clusters of words 
```{r}
set.seed(2016)

word_cors %>%
  filter(correlation > .15) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void()
```

