---
title: "chapter3 examples"
author: "Hao He"
date: "2022-10-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(tidytext)
library(stringr)
library(tidyr)
```

# Analyzing word and document frequency: tf-idf

## Term frequency (tf) and inverse document frequency (idf) 

tf in Jane Austen’s novels
```{r}
library(dplyr)
library(janeaustenr)
library(tidytext)

book_words <- austen_books() %>%
  unnest_tokens(word, text) %>%
  count(book, word, sort = TRUE)

total_words <- book_words %>% 
  group_by(book) %>% 
  summarize(total = sum(n))

book_words <- left_join(book_words, total_words)

book_words
#> # A tibble: 40,379 × 4
#>    book              word      n  total
#>    <fct>             <chr> <int>  <int>
#>  1 Mansfield Park    the    6206 160460
#>  2 Mansfield Park    to     5475 160460
#>  3 Mansfield Park    and    5438 160460
#>  4 Emma              to     5239 160996
#>  5 Emma              the    5201 160996
#>  6 Emma              and    4896 160996
#>  7 Mansfield Park    of     4778 160460
#>  8 Pride & Prejudice the    4331 122204
#>  9 Emma              of     4291 160996
#> 10 Pride & Prejudice to     4162 122204
#> # … with 40,369 more rows
```

plot Term frequency distribution in Jane Austen’s novels
```{r}
library(ggplot2)

ggplot(book_words, aes(n/total, fill = book)) +
  geom_histogram(show.legend = FALSE) +
  xlim(NA, 0.0009) +
  facet_wrap(~book, ncol = 2, scales = "free_y")
```
 These plots exhibit similar distributions for all the novels, *with many words that occur rarely and fewer words that occur frequently*.

## Zipf’s law
Zipf’s law states that the frequency that a word appears is inversely proportional to its rank.

### Zipf’s law with Jane Austen’s novels 
```{r}
freq_by_rank <- book_words %>% 
  group_by(book) %>% 
  mutate(rank = row_number(), 
         `term frequency` = n/total) %>%
  ungroup()

freq_by_rank
```

Zipf’s law is often visualized by plotting rank on the x-axis and term frequency on the y-axis, *on logarithmic scales*. Plotting this way, an inversely proportional relationship will have a *constant, negative* slope.
```{r}
# log-log coordinates
freq_by_rank %>% 
  ggplot(aes(rank, `term frequency`, color = book)) + 
  geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE) + 
  scale_x_log10() +
  scale_y_log10()
```

```{r}
rank_subset <- freq_by_rank %>% 
  filter(rank < 500,
         rank > 10)

lm(log10(`term frequency`) ~ log10(rank), data = rank_subset)
#> 
#> Call:
#> lm(formula = log10(`term frequency`) ~ log10(rank), data = rank_subset)
#> 
#> Coefficients:
#> (Intercept)  log10(rank)  
#>     -0.6226      -1.1125
```

```{r}
freq_by_rank %>% 
  ggplot(aes(rank, `term frequency`, color = book)) + 
  geom_abline(intercept = -0.62, slope = -1.1, 
              color = "gray50", linetype = 2) +
  geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE) + 
  scale_x_log10() +
  scale_y_log10()
```

## bind_tf_idf() function

Calculating tf-idf attempts to find the words that are important (i.e., common) in a text, but not too common.

### Jane Austen works
Below, we calculated a total for each book for our explorations in previous sections, but it is not necessary for the bind_tf_idf() function; the table only needs to contain all the words in each document.
```{r}
book_tf_idf <- book_words %>%
  bind_tf_idf(word, book, n)

book_tf_idf
#> # A tibble: 40,379 × 7
#>    book              word      n  total     tf   idf tf_idf
#>    <fct>             <chr> <int>  <int>  <dbl> <dbl>  <dbl>
#>  1 Mansfield Park    the    6206 160460 0.0387     0      0
#>  2 Mansfield Park    to     5475 160460 0.0341     0      0
#>  3 Mansfield Park    and    5438 160460 0.0339     0      0
#>  4 Emma              to     5239 160996 0.0325     0      0
#>  5 Emma              the    5201 160996 0.0323     0      0
#>  6 Emma              and    4896 160996 0.0304     0      0
#>  7 Mansfield Park    of     4778 160460 0.0298     0      0
#>  8 Pride & Prejudice the    4331 122204 0.0354     0      0
#>  9 Emma              of     4291 160996 0.0267     0      0
#> 10 Pride & Prejudice to     4162 122204 0.0341     0      0
#> # … with 40,369 more rows

# idf and thus tf-idf are zero for these extremely common words
```

#### terms with high tf-idf in Jane Austen’s works.
```{r}
book_tf_idf %>%
  select(-total) %>%
  arrange(desc(tf_idf))
#> # A tibble: 40,379 × 6
#>    book                word          n      tf   idf  tf_idf
#>    <fct>               <chr>     <int>   <dbl> <dbl>   <dbl>
#>  1 Sense & Sensibility elinor      623 0.00519  1.79 0.00931
#>  2 Sense & Sensibility marianne    492 0.00410  1.79 0.00735
#>  3 Mansfield Park      crawford    493 0.00307  1.79 0.00551
#>  4 Pride & Prejudice   darcy       373 0.00305  1.79 0.00547
#>  5 Persuasion          elliot      254 0.00304  1.79 0.00544
#>  6 Emma                emma        786 0.00488  1.10 0.00536
#>  7 Northanger Abbey    tilney      196 0.00252  1.79 0.00452
#>  8 Emma                weston      389 0.00242  1.79 0.00433
#>  9 Pride & Prejudice   bennet      294 0.00241  1.79 0.00431
#> 10 Persuasion          wentworth   191 0.00228  1.79 0.00409
#> # … with 40,369 more rows
```


#### visualization for these high tf-idf words 
```{r}
library(forcats)

book_tf_idf %>%
  group_by(book) %>%
  slice_max(tf_idf, n = 15) %>%
  ungroup() %>%
  ggplot(aes(tf_idf, fct_reorder(word, tf_idf), fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free") +
  labs(x = "tf-idf", y = NULL)
```


## A corpus of physics texts

what terms are important in a different set of works

```{r}
library(gutenbergr)
physics <- gutenberg_download(c(37729, 14725, 13476, 30155), 
                              meta_fields = "author", mirror = "http://mirrors.xmission.com/gutenberg/")

physics_words <- physics %>%
  unnest_tokens(word, text) %>%
  count(author, word, sort = TRUE)

physics_words
#> # A tibble: 12,671 × 3
#>    author              word      n
#>    <chr>               <chr> <int>
#>  1 Galilei, Galileo    the    3760
#>  2 Tesla, Nikola       the    3604
#>  3 Huygens, Christiaan the    3553
#>  4 Einstein, Albert    the    2993
#>  5 Galilei, Galileo    of     2049
#>  6 Einstein, Albert    of     2028
#>  7 Tesla, Nikola       of     1737
#>  8 Huygens, Christiaan of     1708
#>  9 Huygens, Christiaan to     1207
#> 10 Tesla, Nikola       a      1176
#> # … with 12,661 more rows
```

these documents are all different lengths. go ahead and calculate tf-idf, then visualize the high tf-idf 
```{r}

plot_physics <- physics_words %>%
  bind_tf_idf(word, author, n) %>%
  mutate(author = factor(author, levels = c("Galilei, Galileo",
                                            "Huygens, Christiaan", 
                                            "Tesla, Nikola",
                                            "Einstein, Albert")))

plot_physics %>% 
  group_by(author) %>% 
  slice_max(tf_idf, n = 15) %>% 
  ungroup() %>%
  mutate(word = reorder(word, tf_idf)) %>%
  ggplot(aes(tf_idf, word, fill = author)) +
  geom_col(show.legend = FALSE) +
  labs(x = "tf-idf", y = NULL) +
  facet_wrap(~author, ncol = 2, scales = "free")
```
analysis with "K" in the Einsten Text
```{r}
library(stringr)

#str_detect: Detect the presence or absence of a pattern in a string.

physics %>% 
  filter(str_detect(text, "_k_")) %>%  
  select(text)

```
further tidying
```{r}
mystopwords <- tibble(word = c("eq", "co", "rc", "ac", "ak", "bn", 
                                   "fig", "file", "cg", "cb", "cm",
                               "ab", "_k", "_k_", "_x"))

physics_words <- anti_join(physics_words, mystopwords, 
                           by = "word")

plot_physics <- physics_words %>%
  bind_tf_idf(word, author, n) %>%
  mutate(word = str_remove_all(word, "_")) %>%
  group_by(author) %>% 
  slice_max(tf_idf, n = 15) %>%
  ungroup() %>%
  mutate(word = fct_reorder(word, tf_idf)) %>%
  mutate(author = factor(author, levels = c("Galilei, Galileo",
                                            "Huygens, Christiaan",
                                            "Tesla, Nikola",
                                            "Einstein, Albert")))

ggplot(plot_physics, aes(tf_idf, word, fill = author)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~author, ncol = 2, scales = "free") +
  labs(x = "tf-idf", y = NULL)
```
The Jane Austen and physics examples in this chapter did not have much overlap in words with high tf-idf across categories (books, authors). If you find you do share words with high tf-idf across categories, you may want to use reorder_within() and scale_*_reordered() to create visualizations
